---
title: "Landscape Genetics Week 1 R homework"
author: "Erika"
date: "1/21/2020"
output: html_document
---

This is the .Rmd file in which I am doing the Landscape Genetics assignments for week 1. All of them require use of the LandGenCourse package

```{r}
require(LandGenCourse)
```
Now activate swirl for the lessons
```{r}
require(swirl)
swirl()
```

Watching a video from week 0: Introduction to RNotebooks

Continuing where I left off on the tutorial for brining genetic data into R.


```{r}
rm(list = ls())
```
Don't try to run swirl from within the .Rmd.  Stalls.

Now I'm going over some of the worked examples and am going to type some of the code just to help it sink in.  The first example, Week 0: Intro to R programming, is basically review.  But what the heck.  Here's some code from it:

Random numbers and distributions

Examine the `rnorm()`,  `rpois()` and `rchisq()` functions:

Ten random numbers from a normal distribution:
```{r}
rnorm(10)
```
Ten random numbers from a normal distribution with designated mean and standard deviation:
```{r}
rnorm(10, mean = 35, sd = 4)
```
Now into new territory: A poisson distribution with designated mean
```{r}
rpois(10,lambda = 2)
```
And the Chi-square distribution with 1 degree of freedom:
```{r}
rchisq(10, df = 1)
```
Coercing variables to numeric:
Start with data that are defined as a set of characters:
```{r}
x <- c("42", "99")
```
And now coerce to numeric
```{r}
y <- as.numeric(x)
```
Some details on character variables:
Create a chr variable and check how many characters it has:
```{r}
Erika <-"Erika L. Barthelmess"
nchar(Erika)
```
```{r}
nchar(" \t ")
```
Concatenation of characters:
make some character vars:
```{r}
a<-"Erika"
b<-"loves"
c<-"labs!"
#put them into one variable
terms<-c(a,b,c)
terms
```
Now make terms into a single entity with `paste()`:
```{r}
paste(terms, collapse = " ")
```
```{r}
paste(a,b)
```
```{r}
paste(a,b, sep = " really ")
```
Logical types:
```{r}
canThrow<-c(FALSE,TRUE, TRUE, FALSE, FALSE)
canThrow
```
We can implement logical conditions on variables, as well:
```{r}
stable<-c("GRIII" == 0, nchar("Marshawn")==8)
stable
```
We often use logical types to serve as indices for vectors.  For instance:
```{r}
data<-rnorm(20)
data
```
What if you wanted just the non-negative values of data?
```{r}
data[data >0]
```
Let's look at the modulus operator which provides the remainder of a division:
```{r}
1:20 %% 2
```
##Data Containers
###Vectors
You cannot mix data types in a vector.

```{r}
x<-c(1,2,3)
x
```

```{r}
y<-c(TRUE, TRUE, FALSE)
y
```
```{r}
z<-c("I", "am", "not", "a", "looser")
z
```
All of these were acceptable vectors.
If you try to mix data types, all will be coerced to character:
```{r}
w<-c(TRUE, "1", pi, ls())
w
```
```{r}
class(w)
```
We access elements of a vector with the `[ ]` notation.
```{r}
x
```
```{r}
x[1]<-3
x[2]<-1
x[3]<-2
x

```
###Matrices
Create an empty matrix:
```{r}
matrix(nrow=2, ncol = 2)
```
Or prepopulate one with values:
```{r}
matrix(1:4, nrow=2)
```
We can use some other functions to help create numerical matrices:
```{r}
indices<-cbind(rep(1:2, each = 3), rep(1:3, times = 2), rep(5, length.out = 6))
indices
```
###Lists

